MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
updated bib and ssp section

@@

\subsection{Secure Simple Pairing (SSP)}
Secure Simple Pairing (SSP) was introduced in revision 2.1 and has remained largely unchanged in the subsequent versions, although some of the authentication protocols have changed \cite{barnickel2012implementing}.

SSP has 4 association models:

\textbf{Numeric Comparison}: a 6 digit number is displayed on both devices and a user confirms that the numbers match\\
\textbf{Passkey Entry}: designed when one device has input (keyboard) and the other mostly display; the device that has the display shows a 6 digit number, which the user types in on the input device.\\
\textbf{Just Works}: one device has no input or display; the user must accept the connection without being able to visualize that the numbers are the same (more in nist)\\
\textbf{Out of Band (OOB)}: designed to connect when two devices are touched together, (e.g. Near Field Communication or NFC)\\

TODO 5 steps of pairing protocol

>>>>

threat for MITM attacks is high \cite{sandhya2012analysis}

@@

\subsection{Secure Simple Pairing (SSP)}
Secure Simple Pairing (SSP) was introduced in revision 2.1 and has remained largely unchanged in the subsequent versions, although some of the authentication protocols have changed \cite{barnickel2012implementing}. The original purpose of SSP was to simplify the pairing process for the end-user and to improve security, especially against MITM attacks \cite{sandhya2012analysis}. In order to simplify the process, 4 different association modes were created, and are used depending on the capabilities of the devices. The 4 association models are as follows:

\textbf{Numeric Comparison}: a 6 digit number is displayed on both devices and a user confirms that the numbers match (this is designed for devices that both have display and input capabilities)\\\\
\textbf{Passkey Entry}: designed when one device has input (keyboard) and the other mostly display; the device that has the display shows a 6 digit number, which the user types in on the input device.\\\\
\textbf{Just Works}: one device has no input or display; the user must accept the connection without being able to visualize that the numbers are the same (more in nist)\\\\
\textbf{Out of Band (OOB)}: designed to connect when two devices are touched together, (e.g. Near Field Communication or NFC)\\\\
%TODO 5 steps of pairing protocol
